### 2013-11-13 index.Rmd
Final slides for LCSR conference. Major failure due to outdated browser.

>>>>

# Misc links

- [Article code in github](https://github.com/muuankarski/attributions)
- [rustfare-package](http://markuskainu.fi/rustfare/) *- toolbox for R language for open welfare data from Russian Federation*
- [rOpenGov](http://ropengov.github.io/) *-  R Ecosystem for Open Government Data and Computational Social Science*
- [markuskainu.fi](http://markuskainu.fi) *- personal website*

-----
